Flatiron cleaning

### 2021-12-03 Rmd/rdi analysis.Rmd
Fix bug and update

  # 5.Redefine line number based on the original linenumber variable and the surgery date----
  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump F95D860690A93 still weird
  select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
  ungroup() %>%

@@

```{r rule between diagnosis and treatment}
Treatment <- Treatment1 %>% 
  filter(route == "Intravenous") %>% 
  # 1. 60 days rule between diagnosis and treatment # Loss 1
  group_by(patientid) %>% 
  mutate(first_drug_date = first(episodedate)) %>% 
  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
           duration(n=1, units = "days")) %>% 
  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
           duration(n=1, units = "days")) %>% 
  ungroup() %>% 
  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
           duration(n=1, units = "days")
  ) %>% 
  group_by(patientid) %>% 
  mutate(had_carbo_pacli = case_when(
    drugname == "paclitaxel" |
      drugname == "carboplatin"             ~ "Yes"
  )) %>% 
  fill(had_carbo_pacli, .direction = "updown") %>% 
  ungroup() %>% 
  mutate(interval_surgery_to_adj_start = case_when(
      chemotherapy_type == "Adjuvant" &
        linenumber_adj == 1       
      ~ interval(start = surgerydate, end = linestartdate_new) / duration(n = 1, units = "months")
    ),
  ) %>% 
  group_by(patientid) %>% 
  mutate(neo_more_more_than_1line = case_when(
    chemotherapy_type == "Neoadjuvant" &
           linenumber_new != 1                 ~ "exclude"
  )) %>% 
  fill(neo_more_more_than_1line, .direction = "updown") %>% 
  ungroup() %>% 
  mutate(whole_frontline_is_maintenance = case_when(
    (linenumber_new == 1 &
    ismaintenancetherapy == "TRUE") |
    (linenumber_new == 2 &
      therapy == "Upfront Chemo" &
    ismaintenancetherapy == "TRUE")            ~ "exclude"
  )) %>% 
  group_by(patientid) %>% 
  fill(whole_frontline_is_maintenance, .direction = "updown") %>% 
  ungroup() %>% 
  mutate(too_many_cycle = case_when(
    (linenumber_new == 1 &
       therapy == "Upfront Chemo" &
       total_cycle_increment > 6) |

@@

      (linenumber_new == 1 &
         therapy == "Upfront Surgery"))
    ~ "exclude"
  )) %>% 
  group_by(patientid) %>%
  fill(wrong_pacli_dosedense, .direction = "updown") %>% 
  ungroup()

@@

```{r RDI calculation}
Frontline <- Treatment %>% 
  # filter(chemotherapy_type == "Neoadjuvant" |
  #          (chemotherapy_type == "Adjuvant" &
  #             linenumber_adj == 1)) %>%

@@

```{r RDI calculation group}
Frontline <- Frontline %>% 
  # general
  mutate(RDI_grp = case_when(
    mean_RDI_per_drug >= 0.85              ~ "Adequate dosing",
    mean_RDI_per_drug < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_drug < 0.75               ~ "Highly underdosed",
    mean_RDI_per_drug >= 0.75 &
      mean_RDI_per_drug < 0.85             ~ "Underdosed",
    mean_RDI_per_drug >= 0.85 &
      mean_RDI_per_drug < 1.1              ~ "Adequate dosing",
    mean_RDI_per_drug >= 1.1               ~ "Overdosing"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          levels = c("Adequate dosing",
                                     "Underdosed", 
                                     "Highly underdosed",
                                     "Overdosing"))) %>% 
  # separated
  mutate(RDI_carbo_neo = case_when(
    drugname == "carboplatin" &
      chemotherapy_type == "Neoadjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>% 
  mutate(RDI_pacli_neo = case_when(
    drugname == "paclitaxel" &
      chemotherapy_type == "Neoadjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>% 
  mutate(RDI_carbo_adj = case_when(
    drugname == "carboplatin" &
      chemotherapy_type == "Adjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>% 
  mutate(RDI_pacli_adj = case_when(
    drugname == "paclitaxel" &
      chemotherapy_type == "Adjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>%

@@

  mutate(RDI_carbo_adj_grp = case_when(
    RDI_carbo_adj >= 0.85              ~ "Adequate dosing",
    RDI_carbo_adj < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_carbo_adj_grp = factor(RDI_carbo_adj_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_carbo_adj_grp1 = case_when(
    RDI_carbo_adj < 0.75               ~ "Highly underdosed",
    RDI_carbo_adj >= 0.75 &
      RDI_carbo_adj < 0.85             ~ "Underdosed",
    RDI_carbo_adj >= 0.85 &
      RDI_carbo_adj < 1.1              ~ "Adequate dosing",
    RDI_carbo_adj >= 1.1               ~ "Overdosing"
  )) %>% 
  mutate(RDI_carbo_adj_grp1 = factor(RDI_carbo_adj_grp1, 
                          levels = c("Adequate dosing",
                                     "Underdosed", 
                                     "Highly underdosed",
                                     "Overdosing"))) %>% 
  mutate(RDI_pacli_adj_grp = case_when(
    RDI_pacli_adj >= 0.85              ~ "Adequate dosing",
    RDI_pacli_adj < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_pacli_adj_grp = factor(RDI_pacli_adj_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_pacli_adj_grp1 = case_when(
    RDI_pacli_adj < 0.75               ~ "Highly underdosed",
    RDI_pacli_adj >= 0.75 &
      RDI_pacli_adj < 0.85             ~ "Underdosed",
    RDI_pacli_adj >= 0.85 &
      RDI_pacli_adj < 1.1              ~ "Adequate dosing",
    RDI_pacli_adj >= 1.1               ~ "Overdosing"
  )) %>% 
  mutate(RDI_pacli_adj_grp1 = factor(RDI_pacli_adj_grp1, 
                          levels = c("Adequate dosing",
                                     "Underdosed", 
                                     "Highly underdosed",
                                     "Overdosing")))
Frontline %>% distinct(patientid) %>% nrow()
```

```{r Frontline_adjusted}
Frontline_adjusted <- Frontline %>% 
  group_by(patientid) %>% 
  fill(RDI_carbo_neo, RDI_carbo_neo_grp, RDI_carbo_neo_grp1, 
       RDI_pacli_neo, RDI_pacli_neo_grp, RDI_pacli_neo_grp1, 
       RDI_carbo_adj, RDI_carbo_adj_grp, RDI_carbo_adj_grp1, 
       RDI_pacli_adj, RDI_pacli_adj_grp, RDI_pacli_adj_grp1, 
       .direction = "downup") %>% 
  distinct(patientid, .keep_all = TRUE)
```

@@

Are excluded :  
-	Borderline cases (not invasive ovarian cancer)  
-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)  
```{r}
flatiron_rec <- Frontline_adjusted %>% 
  mutate(flatiron_rules = case_when(
    days_at_first_drug > 90 | 
      days_at_surg > 90                          ~ "exclude",
    thirty_days_exclusion <= 30                  ~ "exclude",
    exclude == "1"                               ~ "exclude"
  )) %>%
  group_by(patientid) %>% 
  fill(flatiron_rules, .direction = "downup") %>% 
  ungroup()

flatiron_rec <- flatiron_rec %>% 
  filter(is.na(flatiron_rules))
```

@@

- exclude patients whose histology is unknown  
- remove chemotherapy only patients
- include only patients who received platin and/or taxane
- exclude patients who only received neo + surgery
- include patients with single or dual P/T +/- Bev as frontline treatment
```{r}
study_criteria <- flatiron_rec %>% 
  filter(!is.na(histology)) # loss 287 ################## Will do when bind to drugs

@@

study_criteria <- study_criteria %>%
  # Remove patients with other linename
  filter((linenumber_new == 1 &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin")) |
          (linenumber_new == 2 &
          therapy == "Upfront Chemo" &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Carboplatin"))
         )
```

@@

test <- Frontline %>% 
  filter(wrong_pacli_dosedense == "exclude")

wrong_pacli_dosedense <- Treatment %>% arrange(patientid, episodedate, drugname) %>% 
  filter(str_detect(patientid, paste(test$patientid, collapse = "|"))) %>% 
  select(patientid, chemotherapy_type, therapy, episodedate, drugname, ismaintenancetherapy, linenumber_new, cycle_increment, too_many_cycle, dose_dense, wrong_pacli_dosedense,  linename)
```
**We have `r Frontline %>% distinct(patientid) %>% nrow()` patients.**

@@

`r Frontline %>% filter(str_detect(linename, "Car") & drugname == "cisplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line.  
`r Frontline %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line.

@@

`r Frontline %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.  
<!-- I am removing these patients   -->

<!-- Patients left: -->
```{r}
# remove_switch1 <- therapy_line %>% 
#   filter(
#     str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1
#   ) %>%
#   distinct(patientid)
# remove_switch1 <- paste(remove_switch1$patientid, collapse = "|")
# 
# therapy_line <- therapy_line %>% 
#   # remove these patients who switched C > C 
#   filter(!str_detect(patientid, remove_switch1))
# therapy_line %>% distinct(patientid) %>% nrow()
```

@@

## **The final number of patients in the dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**

@@

### Number of line in treatment and cycle in frontline  
Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
in upfront neo
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment) %>% 
  tbl_summary()
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
  arrange(desc(cycle_increment)) %>% 
  mutate(cycle_increment = as.numeric(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```

Number of Adjuvant line in patients with upfront neo
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary(label = list(cycle_increment ~ "cycle number during the adjuvant course in Upfront Chemo setting"))

Treatment %>% 
  filter(therapy == "Upfront Chemo") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(total_cycle_increment = factor(total_cycle_increment)) %>% 
  arrange(desc(total_cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(total_cycle_increment) %>% 
  tbl_summary(label = list(total_cycle_increment ~ "total cycle number in Upfront Chemo setting"))
```
Number of Adjuvant line in patients with upfront surgery
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
<br>

@@

## Adjusted by other drug
### RDI group
`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat` 
```{r Table 5 HR adjusted rdi group adjusted by other drug}
tbl2 <- Frontline_adjusted %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline_adjusted %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059).

>>>>

  # 5.Redefine line number based on the original linenumber variable and the surgery date----
  mutate(linenumber_n = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  
  group_by(patientid, linenumber_n, ismaintenancetherapy) %>% 
  mutate(maint_rank = row_number(ismaintenancetherapy),
         maint_rank = ifelse(maint_rank == 1, 1, 0)) %>%

  group_by(patientid) %>% 
  mutate(linenumber_new = cumsum(maint_rank)) %>%  
  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump F95D860690A93 still weird F0F1324B863A8
  select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
  ungroup() %>%

@@

```{r rule between diagnosis and treatment}
Treatment <- Treatment1 %>% 
  filter(route == "Intravenous") %>% 
  # 1. 60 days rule between diagnosis and treatment # Loss 1
  group_by(patientid) %>% 
  mutate(first_drug_date = first(episodedate)) %>% 
  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
           duration(n=1, units = "days")) %>% 
  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
           duration(n=1, units = "days")) %>% 
  mutate(days_at_first_treatment = case_when(
    therapy == "Upfront Chemo" |
      therapy == "Chemotherapy only"             ~ interval(start = diagnosisdate, end = first_drug_date)/
           duration(n=1, units = "days"),
    therapy == "Upfront Surgery" |
      therapy == "Surgery Only"                  ~ interval(start = diagnosisdate, end = surgerydate)/
           duration(n=1, units = "days")
  )) %>% 
  ungroup() %>% 
  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
           duration(n=1, units = "days")
  ) %>% 
  group_by(patientid) %>% 
  mutate(had_carbo_pacli = case_when(
    drugname == "paclitaxel" |
      drugname == "carboplatin"             ~ "Yes"
  )) %>% 
  fill(had_carbo_pacli, .direction = "updown") %>% 
  ungroup() %>% 
  mutate(interval_surgery_to_adj_start = case_when(
      chemotherapy_type == "Adjuvant" &
        linenumber_adj == 1       
      ~ interval(start = surgerydate, end = linestartdate_new) / duration(n = 1, units = "months")
    ),
  ) %>% 
  group_by(patientid) %>% 
  mutate(neo_more_more_than_1line = case_when(
    chemotherapy_type == "Neoadjuvant" &
           linenumber_new != 1                 ~ "exclude"
  )) %>% 
  fill(neo_more_more_than_1line, .direction = "updown") %>% 
  ungroup() %>% 
  mutate(whole_frontline_is_maintenance = case_when(
    (linenumber_new == 1 &
    ismaintenancetherapy == "TRUE") |
    (linenumber_new == 2 &
      therapy == "Upfront Chemo" &
    ismaintenancetherapy == "TRUE")            ~ "exclude"
  )) %>% 
  group_by(patientid) %>% 
  fill(whole_frontline_is_maintenance, .direction = "updown") %>% 
  ungroup() %>% 
  mutate(too_many_cycle = case_when(
    (linenumber_new == 1 &
       therapy == "Upfront Chemo" &
       total_cycle_increment > 6) |

@@

      (linenumber_new == 1 &
         therapy == "Upfront Surgery"))
    ~ "exclude"
  )) %>% 
  group_by(patientid) %>%
  fill(wrong_pacli_dosedense, .direction = "updown") %>% 
  ungroup() %>% 
  mutate(switch_drugs = case_when(
    str_detect(linename, "Pacli") & 
      drugname == "docetaxel" & 
      linenumber_adj == 1                      ~ "exclude",
    str_detect(linename, "Car") & 
      drugname == "cisplatin" & 
      linenumber_adj == 1                      ~ "exclude"
  )) %>% 
  group_by(patientid) %>%
  fill(switch_drugs, .direction = "updown") %>% 
  ungroup() %>%

  mutate(line_keep = case_when(# F002B429BE6C6
    (linenumber_adj == 1 &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin"))            ~ "include"
  )) %>% 
  group_by(patientid) %>%
  fill(line_keep, .direction = "updown") %>% 
  ungroup() %>% 
  mutate(flatiron_rules = case_when(
    days_at_first_treatment > 90                          ~ "exclude",
    thirty_days_exclusion <= 30                  ~ "exclude",
    exclude == "1"                               ~ "exclude"
  )) %>%
  group_by(patientid) %>% 
  fill(flatiron_rules, .direction = "downup") %>% 
  ungroup()

@@

```{r RDI calculation}
RDI_data <- Treatment %>% 
  # filter(chemotherapy_type == "Neoadjuvant" |
  #          (chemotherapy_type == "Adjuvant" &
  #             linenumber_adj == 1)) %>%

@@

```{r RDI calculation group}
RDI_data <- RDI_data %>% 
  # general
  mutate(RDI_grp = case_when(
    mean_RDI_per_drug >= 0.85              ~ "Adequate dosing",
    mean_RDI_per_drug < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_drug < 0.75               ~ "Highly underdosed",
    mean_RDI_per_drug >= 0.75 &
      mean_RDI_per_drug < 0.85             ~ "Underdosed",
    mean_RDI_per_drug >= 0.85 &
      mean_RDI_per_drug < 1.1              ~ "Adequate dosing",
    mean_RDI_per_drug >= 1.1               ~ "Overdosing"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          levels = c("Adequate dosing",
                                     "Underdosed", 
                                     "Highly underdosed",
                                     "Overdosing"))) %>% 
  # separated
  mutate(RDI_carbo_neo = case_when(
    drugname == "carboplatin" &
      chemotherapy_type == "Neoadjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>% 
  mutate(RDI_pacli_neo = case_when(
    drugname == "paclitaxel" &
      chemotherapy_type == "Neoadjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>% 
  mutate(RDI_carbo_adj = case_when(
    drugname == "carboplatin" &
      chemotherapy_type == "Adjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>% 
  mutate(RDI_pacli_adj = case_when(
    drugname == "paclitaxel" &
      chemotherapy_type == "Adjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>%

@@

  mutate(RDI_carbo_adj_grp = case_when(
    RDI_carbo_adj >= 0.85              ~ "Adequate dosing",
    RDI_carbo_adj < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_carbo_adj_grp = factor(RDI_carbo_adj_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_carbo_adj_grp1 = case_when(
    RDI_carbo_adj < 0.75               ~ "Highly underdosed",
    RDI_carbo_adj >= 0.75 &
      RDI_carbo_adj < 0.85             ~ "Underdosed",
    RDI_carbo_adj >= 0.85 &
      RDI_carbo_adj < 1.1              ~ "Adequate dosing",
    RDI_carbo_adj >= 1.1               ~ "Overdosing"
  )) %>% 
  mutate(RDI_carbo_adj_grp1 = factor(RDI_carbo_adj_grp1, 
                          levels = c("Adequate dosing",
                                     "Underdosed", 
                                     "Highly underdosed",
                                     "Overdosing"))) %>% 
  mutate(RDI_pacli_adj_grp = case_when(
    RDI_pacli_adj >= 0.85              ~ "Adequate dosing",
    RDI_pacli_adj < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_pacli_adj_grp = factor(RDI_pacli_adj_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_pacli_adj_grp1 = case_when(
    RDI_pacli_adj < 0.75               ~ "Highly underdosed",
    RDI_pacli_adj >= 0.75 &
      RDI_pacli_adj < 0.85             ~ "Underdosed",
    RDI_pacli_adj >= 0.85 &
      RDI_pacli_adj < 1.1              ~ "Adequate dosing",
    RDI_pacli_adj >= 1.1               ~ "Overdosing"
  )) %>% 
  mutate(RDI_pacli_adj_grp1 = factor(RDI_pacli_adj_grp1, 
                          levels = c("Adequate dosing",
                                     "Underdosed", 
                                     "Highly underdosed",
                                     "Overdosing")))
RDI_data %>% distinct(patientid) %>% nrow()
```

```{r Frontline_adjusted}
Frontline_adjusted <- RDI_data %>% 
  group_by(patientid) %>% 
  fill(RDI_carbo_neo, RDI_carbo_neo_grp, RDI_carbo_neo_grp1, 
       RDI_pacli_neo, RDI_pacli_neo_grp, RDI_pacli_neo_grp1, 
       RDI_carbo_adj, RDI_carbo_adj_grp, RDI_carbo_adj_grp1, 
       RDI_pacli_adj, RDI_pacli_adj_grp, RDI_pacli_adj_grp1, 
       .direction = "downup") %>% 
  ungroup() %>% 
  distinct(patientid, .keep_all = TRUE)
```

@@

Are excluded :  
-	Borderline cases (not invasive ovarian cancer)  
-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)  
```{r}
flatiron_rec <- Frontline_adjusted %>% 
  filter(is.na(flatiron_rules))
```

@@

- exclude patients whose histology is unknown  
- remove chemotherapy only patients
- include only patients who received platin and/or taxane
- exclude patients who only received neo + surgery
- include patients with single or dual P/T +/- Bev as frontline treatment
```{r}
study_criteria <- flatiron_rec %>% 
  filter(!is.na(histology))

@@

study_criteria <- study_criteria %>%
  filter(line_keep == "include")
  # Remove patients with other linename
  # filter((linenumber_new == 1 &
  #          (linename == "Carboplatin,Paclitaxel" |
  #          linename == "Bevacizumab,Carboplatin,Paclitaxel" |
  #          linename == "Carboplatin" |
  #          linename == "Paclitaxel" |
  #          linename == "Bevacizumab,Paclitaxel" |
  #          linename == "Bevacizumab,Carboplatin")) |
  #         (linenumber_new == 2 &
  #         therapy == "Upfront Chemo" &
  #          (linename == "Carboplatin,Paclitaxel" |
  #          linename == "Bevacizumab,Carboplatin,Paclitaxel" |
  #          linename == "Carboplatin" |
  #          linename == "Bevacizumab,Paclitaxel" |
  #          linename == "Paclitaxel" |
  #          linename == "Bevacizumab,Carboplatin"))
  #        )
```

@@

# test <- Frontline %>% 
#   filter(wrong_pacli_dosedense == "exclude")
# 
# wrong_pacli_dosedense <- Treatment %>% arrange(patientid, episodedate, drugname) %>% 
#   filter(str_detect(patientid, paste(test$patientid, collapse = "|"))) %>% 
#   select(patientid, chemotherapy_type, therapy, episodedate, drugname, ismaintenancetherapy, linenumber_new, cycle_increment, too_many_cycle, dose_dense, wrong_pacli_dosedense,  linename)
```
**We have `r Frontline %>% distinct(patientid) %>% nrow()` patients.**

@@

<!-- `r Frontline %>% filter(str_detect(linename, "Car") & drugname == "cisplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line.   -->
<!-- `r Frontline %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line.   -->

@@

<!-- `r Frontline %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.   -->
<!-- I am removing these patients   -->

<!-- Patients left: -->
```{r}
Frontline <- Frontline %>%
  filter(is.na(switch_drugs))
```

@@

# **The final number of patients in the dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**

@@

### Number of line in treatment and cycle in frontline  
Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
in upfront neo
```{r}
RDI_data <- 
  Treatment %>% 
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
  arrange(patientid, episodedate, drugname)

RDI_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
RDI_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment) %>% 
  tbl_summary()
RDI_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
  arrange(desc(cycle_increment)) %>% 
  mutate(cycle_increment = as.numeric(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```

Number of Adjuvant line in patients with upfront neo
```{r}
RDI_data %>% 
  filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

RDI_data %>% 
  filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary(label = list(cycle_increment ~ "cycle number during the adjuvant course in Upfront Chemo setting"))

RDI_data %>% 
  filter(therapy == "Upfront Chemo") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(total_cycle_increment = factor(total_cycle_increment)) %>% 
  arrange(desc(total_cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(total_cycle_increment) %>% 
  tbl_summary(label = list(total_cycle_increment ~ "total cycle number in Upfront Chemo setting"))
```
Number of Adjuvant line in patients with upfront surgery
```{r}
RDI_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

RDI_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
<br>

@@

## Adjusted by other drug
### RDI group
`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat` 
```{r Table 5 HR adjusted rdi group adjusted by other drug}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059).
